Local Search, Brute-Force and Recursion for Selection Operator\thanks{This work was not supported by Velbazhd Software LLC and Bulgarian Ministry of Education and Science.}

### 2020-04-13 Local-Search-Brute-Force-and-Recursion-for-Selection-Operator/paper.tex
Experiments and results were added.

\usepackage{balance}
\IEEEoverridecommandlockouts 
\usepackage[dvips]{graphicx}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{listings}
\usepackage[OT4,T1]{fontenc}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{url}
\usepackage{multirow}
\usepackage{caption}

@@

\begin{algorithm}[H]
\includegraphics[width=1.0\hsize]{fig01.eps}
\caption{Local Search}
\label{algo01}
\end{algorithm}

@@

>>>>

\usepackage{balance}
\IEEEoverridecommandlockouts 
\usepackage[dvips]{graphicx}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{listings}
\usepackage[OT4,T1]{fontenc}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{url}
\usepackage{multirow}
\usepackage{caption}
\usepackage{diagbox}

@@

\begin{algorithm}[tbp]
\includegraphics[width=1.0\hsize]{fig01.eps}
\caption{Local search extension.}
\label{algo01}
\end{algorithm}

@@

All experiments are done in 10000-dimensional solutions space. As benchmark functions are selected five very well known functions: Michalewicz, Ackley, Schwefel, Rastrigin, and Griewank. Algorithms are tested with levels of recursive descent from 2 to 7 and with population size from 2 to 11. Table \ref{tab01} shows the calculation time used in both algorithms for the configuration of recursive descent 7 and population size 11. Table \ref{tab02} shows the total number of individuals evaluation (fitness value calculation) in both algorithms for the configuration of recursive descent 7 and population size 11. Because of the limits for the length of this paper the other configurations for recursive level and population size are not presented here, but can be found at this URL address: https://github.com/TodorBalabanov/FedCSIS-Conference-on-Computer-Science-and-Information-Systems-2020/tree/master/Local-Search-Brute-Force-and-Recursion-for-Selection-Operator

\begin{table*}[tbp]
\caption{Calculation time [ms] for recursion level of 7 and population size of 11.}
\centering
\begin{tabular}{|@{\vrule width0ptheight9pt\enspace}l|c|c|c|c|c|c|}
\hline
\hfil\bf \backslashbox{Algorithm}{Funcition}  & \bf Michalewicz & \bf Ackley & \bf Schwefel & \bf Rastrigin & \bf Griewank \\
\hline
\bf Local Search & 1062492546 & 531027435 & 533232986 & 507650704 & 592370933 \\
\hline
\bf Brute-Force & 403141211 & 166733879 & 175069174 & 159862955 & 218428047 \\
\hline
\end{tabular}
\label{tab01}
\end{table*}

\begin{table*}[tbp]
\caption{Number of fitness calculations for recursion level of 7 and population size of 11.}
\centering
\begin{tabular}{|@{\vrule width0ptheight9pt\enspace}l|c|c|c|c|c|c|}
\hline
\hfil\bf \backslashbox{Algorithm}{Funcition}  & \bf Michalewicz & \bf Ackley & \bf Schwefel & \bf Rastrigin & \bf Griewank \\
\hline
\bf Local Search & 641125639 & 641024362 & 640914978 & 641092606 & 640830762 \\
\hline
\bf Brute-Force & 235794757 & 235794757 & 235794757 & 235794757 & 235794757 \\
\hline
\end{tabular}
\label{tab02}
\end{table*}

\begin{table*}[tbp]
\caption{Suboptimal values found for recursion level of 7 and population size of 11.}
\centering
\begin{tabular}{|@{\vrule width0ptheight9pt\enspace}l|c|c|c|c|c|c|}
\hline
\hfil\bf \backslashbox{Algorithm}{Funcition}  & \bf Michalewicz & \bf Ackley & \bf Schwefel & \bf Rastrigin & \bf Griewank \\
\hline
\bf Local Search & -1484.7137949531716 & 21.09334816052046 & 3877924.0971615044 & 170204.87849875208 & 259918.15469527297 \\
\hline
\bf Brute-Force & -1439.2296970724608 & 21.114702255301292 & 3919318.729777085 & 171780.33307271387 & 262621.61053178157 \\
\hline
\end{tabular}
\label{tab03}
\end{table*}

Suboptimal values achieved by both algorithms are presented in Fig. \ref{fig01}-\ref{fig10}. The presented information includes all experimental combinations of recursive descent levels and population sizes. Table \ref{tab03} shows suboptimal values found by both algorithms for the configuration of recursive descent 7 and population size 11. Values achieved with the local search extension are closer to the global optimums.

\begin{figure}[tbp]
\centering
\includegraphics[width=1.0\hsize]{fig03.eps}
\caption{Michalewicz - Local Search}
\label{fig01}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=1.0\hsize]{fig06.eps}
\caption{Ackley - Local Search}
\label{fig02}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=1.0\hsize]{fig09.eps}
\caption{Schwefel - Local Search}
\label{fig03}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=1.0\hsize]{fig12.eps}
\caption{Rastrigin - Local Search}
\label{fig04}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=1.0\hsize]{fig15.eps}
\caption{Griewank - Local Search}
\label{fig05}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=1.0\hsize]{fig18.eps}
\caption{Michalewicz - Brute Force}
\label{fig06}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=1.0\hsize]{fig21.eps}
\caption{Ackley - Brute Force}
\label{fig07}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=1.0\hsize]{fig24.eps}
\caption{Schwefel - Brute Force}
\label{fig08}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=1.0\hsize]{fig27.eps}
\caption{Rastrigin - Brute Force}
\label{fig09}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=1.0\hsize]{fig30.eps}
\caption{Griewank - Brute Force}
\label{fig10}
\end{figure}
